\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
Firewalls!

\section*{Firewall Traversal}
% TODO

>>>>

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We plan on
reimplementing something similar to \texttt{chownat} (http://samy.pl/chownat/),
which appears to be a standard way to do this.
